Spin canonical divisors of log stacky curves

### 2015-06-25 stacky_write_up/spin_cring.tex
compile error fixed
fix bad refs, add gitignore to beamer folder

\begin{itemize}
\item[(a)] $R_{\halfcan}$ is generated over $R_{\halfcan'}$ by elements $y_1, \ldots, y_n$ such that $y_i$ lies in  
degree $d_i$ and has a pole at $P$ of degree $c_i$

@@

\begin{thm}
\label{thm:general_generators_relations}
Let $g \geq 2$ and let $(\sx, \Delta, \halfcan)$ log spin curve over a perfect field $k$, so
that $\sx$ has signature $\sigma = (g; e_1, \ldots, e_r; \delta)$. Then the
canonical ring

@@

\begin{proof}
Let $\halfcan_X \in \di X$ satisfy $2\halfcan_X + 2 K_X + \Delta$. By Lemma ~\ref{lem:generation_5} and Proposition ~\ref{prop:relation_11}, the theorem holds for $(\sx, \Delta, \halfcan_X)$. Next, consider a divisor of the form $\halfcan' = \halfcan_X + \frac{1}{3}P_i$. Then, the theorem holds for $(\sx,\Delta, \halfcan')$ by Lemma ~\ref{lem:sat-two-induction-high-genus} if $P_i$ is a basepoint of $\halfcan'$ or by Lemma ~\ref{deg1-sat-ind} if $P_i$ is not a basepoint of $L'$. Note, in the case $P$ is a not basepoint of $\halfcan'$, Equation ~\ref{eqn:deg1-sat-ind} holds by Riemann Roch, and the fact that $d \geq 3$.

In this case, we claim $(\sx',L',\{1\})$ is admissible. Indeed, (Ad-i) holds by part (a) of Lemmas ~\ref{lem:sat-two-induction-high-genus} and ~\ref{deg1-sat-ind}, (Ad-ii) holds by part (b) of Lemmas ~\ref{lem:sat-two-induction-high-genus} and ~\ref{deg1-sat-ind}, and (Ad-iii) holds as $5\deg L \geq 5(g-1)> 2g-1.$ Therefore, by Lemma ~\ref{lem:n-3s-admissible}, Any triple of the form $(\sx',L',\{1,\ldots, r\})$ is admissible, with $e_1 = \cdots = e_r = 3$. Hence, by Corollary ~\ref{cor:raise-stacky-order}, this theorem holds for all log spin curves $(\sx, L, J).$ 
\end{proof}

>>>>

\begin{enumerate}
\item[(a)] $R_{\halfcan}$ is generated over $R_{\halfcan'}$ by elements $y_1, \ldots, y_n$ such that $y_i$ lies in  
degree $d_i$ and has a pole at $P$ of degree $c_i$

@@

\begin{thm}
\label{thm:high_generators_relations}
Let $g \geq 2$ and let $(\sx, \Delta, \halfcan)$ log spin curve over a perfect field $k$, so
that $\sx$ has signature $\sigma = (g; e_1, \ldots, e_r; \delta)$. Then the
canonical ring

@@

\begin{proof}
Let $\halfcan_X \in \di X$ satisfy $2\halfcan_X + 2 K_X + \Delta$.
By Lemma ~\ref{lem:generation_5} and Proposition
~\ref{prop:relation_11}, the theorem holds for $(\sx, \Delta,
\halfcan_X)$. Next, consider a divisor of the form $\halfcan' =
\halfcan_X + \frac{1}{3} P_i$. Then, the theorem holds for $(\sx,
\Delta, \halfcan')$ by Lemma ~\ref{lem:sat-two-induction-high-genus}
 if $P_i$ is a basepoint of $\halfcan'$ or by Lemma
~\ref{lem:deg1-sat-ind} if $P_i $ is not a basepoint of $L'$. Note,
in the case $P$  is a not basepoint of $\halfcan'$, Equation
~\ref{eqn:deg1-sat-ind} holds by Riemann Roch, and the fact that $d
\geq 3$.

In this case, we claim $(\sx',L',\{1\})$ is admissible. Indeed, (Ad-
i) holds by part (a) of Lemmas
~\ref{lem:sat-two-induction-high-genus} and ~\ref{lem:deg1-sat-ind},
(Ad-ii) holds by part (b) of Lemmas
~\ref{lem:sat-two-induction-high-genus} and ~\ref{lem:deg1-sat-ind},
and (Ad-iii) holds as $5\deg L \geq 5(g-1)> 2g-1.$ Therefore, by
Lemma ~\ref{lem:n-3s-admissible} , Any triple of the form $(\sx', L',
\{1,\ldots, r\})$ is admissible, with $e_1 = \cdots = e_r = 3$.
Hence, by Corollary ~\ref{cor:raise-stacky-order}, this theorem 
holds for all log spin curves $(\sx, L, J)$. 
\end{proof}
